Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-13 Response.tex

\item
    \begin{itshape}
Authors may also want to point out the loss of accuracy in variable step integrators that can also degrade first-order gradient based methods.  I didn't see this anywhere and it's something that should be acknowledged.  Basically, variable step integrators will introduce artificial "noise" into the gradients:

Pellegrini, E.P., Russell, R.P., On the Accuracy of Trajectory State Transition Matrices, Paper AAS-15-785, AAS/AIAA Astrodynamics Specialist Conference, Vail, CO, Aug 2015
\end{itshape}

Additional detail has been included in the manuscript discussing this potential drawback of variable step integrators.
\begin{correction}
In addition, it has been shown that variable step integrators, such as \texttt{ODE45} in Matlab, tend to degrade first-order gradient based methods, such as those used in~\cref{sec:optimal_control}~\cite{pellegrini2016}.
The fixed step size of the presented variational integrator mitigates the artifical ``noise'' of variable step integration schemes in gradient computation.
\end{correction}
\item 
    \begin{itshape}
"This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods." I disagree that suboptimality is typical of direct methods.  A direct method will typically solve the KKT conditions, which can be directly transcribed into the costates in the optimal control problem.  A direct method fully satisfying the KKT conditions can map to the indirect problem. If you want to strengthen this argument, then you should argue that it applies to direct methods which rely on coarse or suboptimal representations of the control.  For example, a hybrid direct method could use continuous optimal control theory control law, but directly minimize the cost function instead of solving the full TPBVP.  
\end{itshape}

### 2017-07-13 manuscript.tex
Add detail about variable step integration
Reviewer 1 Comment 12

\section{Optimal Control Formulation for Reachability Set}
% introduce method
In this section, an optimal control formulation is presented to determine and design transfers within the three-body problem.
The application of variational integrators to optimal control problems is referred to as computational geometric optimal control.
Our formulation is based on the concept of the reachability set on a \Poincare section.
This method allows one to easily determine potential transfer opportunities by finding set intersections on a lower dimensional space and greatly reduces the design process.
The addition of continuous low thrust propulsion extends the control free design process developed previously and allows for a greater range of potential transfers with a reduced time of flight.

>>>>

In addition, it has been shown that variable step integrators, such as \texttt{ODE45} in Matlab, tend to degrade first-order gradient based methods, such as those used in~\cref{sec:optimal_control}~\cite{pellegrini2016}.
The fixed step size of the presented variational integrator mitigates the artifical ``noise'' of variable step integration schemes in gradient computation.

\section{Optimal Control Formulation for Reachability Set}\label{sec:optimal_control}
% introduce method
In this section, an optimal control formulation is presented to determine and design transfers within the three-body problem.
The application of variational integrators to optimal control problems is referred to as computational geometric optimal control.
Our formulation is based on the concept of the reachability set on a \Poincare section.
This method allows one to easily determine potential transfer opportunities by finding set intersections on a lower dimensional space and greatly reduces the design process.
The addition of continuous low thrust propulsion extends the control free design process developed previously and allows for a greater range of potential transfers with a reduced time of flight.
